Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Fixing my mistake

\subsubsection{Allocating Addresses}
Up to this point, we have not described allocating addresses in stores,
nor handling the time stamp @Time@.
In abstract interpretation, however, these are key ingredients to achieve
analyses with different sensitivities, as well as to perform a finite
state space analysis\cite{Gilray:2016:ACP:2951913.2951936}.
To effectively approximate the runtime behavior, we introduce a finite
program counter @time@ that encodes the program execution history.
We use a list of execution contexts (expressions) to represent this, and
as we will see in Section~\ref{kcfainst}, by applying different @tick@
functions on the timestamp, we are able to obtain a family of analyses.

@@

In $k$-call-sensitive analysis, a history of the last $k$ call sites is
used as a finite program counter.
The history is represented as a list of expressions and embedded
in the allocated addresses.

@@

Similar to the CESK machines, to run (analyze) a program
we first use the @inject@ function to construct the initial state given to the program.
Note that the initial continuation store has a built-in mapping that maps the continuation
address for @Halt@ to an empty set of continuations.
We also provide an empty program counter as our initial time.
\begin{lstlisting}
def inject(e: Expr): State =
  State(e, Map(),
        Store[BAddr, Storable](Map()),
        Store[KAddr, Cont](Map(Halt -> Set())),
        Halt, List())
\end{lstlisting}

>>>>

\subsubsection{Allocating Addresses}
Up to this point, we have not described allocating addresses in stores,
nor handling the time stamp @Time@.
In abstract interpretation, however, these are key ingredients to achieve
analyses with different sensitivities, as well as to perform a finite
state space analysis\cite{Gilray:2016:ACP:2951913.2951936}.
To effectively approximate the runtime behavior, we introduce a finite
program contour @time@ that encodes the program execution history.
We use a list of execution contexts (expressions) to represent this, and
as we will see in Section~\ref{kcfainst}, by applying different @tick@
functions on the timestamp, we are able to obtain a family of analyses.

@@

In $k$-call-sensitive analysis, a history of the last $k$ call sites is
used as a finite program contour.
The history is represented as a list of expressions and embedded
in the allocated addresses.

@@

Similar to the CESK machines, to run (analyze) a program
we first use the @inject@ function to construct the initial state given to the program.
Note that the initial continuation store has a built-in mapping that maps the continuation
address for @Halt@ to an empty set of continuations.
We also provide an empty program contour as our initial time.
\begin{lstlisting}
def inject(e: Expr): State =
  State(e, Map(),
        Store[BAddr, Storable](Map()),
        Store[KAddr, Cont](Map(Halt -> Set())),
        Halt, List())
\end{lstlisting}
